\cvsection{Projects}
\begin{cventries}
    \cventry
    {Machine Learning Engineer}
    {Codeforces Tag Predictor}
    {\href{https://github.com/alexsierra45/codeforce-tag-predictor}{GitHub}}
    {2024}
    {
      \begin{cvitems}
        \item {Implemented a Transformer-based model to predict tags for Codeforces problems as part of a machine learning course project.}
        \item {Trained the model with a comprehensive dataset, optimizing accuracy and reducing loss with advanced regularization techniques.}
        \item {Documented the entire training and prediction pipeline to ensure reproducibility of the experiment.}
      \end{cvitems}
    }
    \cventry
    {Game Simulator Developer}
    {Football Simulator}
    {\href{https://github.com/alexsierra45/football-simulator}{GitHub}}
    {2023}
    {
      \begin{cvitems}
        \item {Designed a football simulator encompassing team management, match tactics, and realistic gameplay simulation.}
        \item {Implemented advanced AI algorithms such as \textbf{Monte Carlo Tree Search} and \textbf{Minimax} to optimize in-game decisions and tactics.}
        \item {Integrated a \textbf{Large Language Model (LLM)} to generate realistic strategies, team formations, and player assignments.}
        \item {Created a dynamic player performance system that adapts based on attributes, tactics, and real-time match events.}
        % \item {Developed a user-friendly interface to make the simulator accessible while maintaining detailed control over team and strategy management.}
      \end{cvitems}
    }
    \cventry
    {Distributed System Architect}
    {Twitt-Py}
    {\href{https://github.com/alexsierra45/twitt-py}{GitHub}}
    {2024}
    {
      \begin{cvitems}
        \item {Designed and implemented a distributed system using the Chord protocol to manage and locate data in a decentralized network.}
        \item {Developed efficient routing and data partitioning logic, ensuring scalability and fault tolerance.}
      \end{cvitems}
    }
  \cventry
    {Compiler Engineer}
    {Hulk Compiler}
    {\href{https://github.com/alexsierra45/hulk-compiler}{GitHub}}
    {2024}
    {
      \begin{cvitems}
        \item {Built a full HULK compiler covering lexical, syntactic, and semantic analysis as part of the Compiler Theory course.}
        \item {Implemented intermediate code generation.}
        \item {Facilitated learning of core compiler concepts with detailed documentation and practical examples.}
      \end{cvitems}
    }

    \cventry
    {Backend Developer}
    {Travel Agency App}
    {\href{https://github.com/alexsierra45/travel-agency}{GitHub}}
    {2023}
    {
      \begin{cvitems}
        \item {Developed a backend application to manage travel agencies, enabling the handling of clients, bookings, and destinations.}
        \item {Designed a RESTful API using clean architecture principles, ensuring scalability and ease of integration with frontends.}
        \item {Integrated an authentication system and role management to ensure security.}
      \end{cvitems}
    }
\end{cventries}
